---
title: | 
  | Assignment 4: Collaborating Together
  | Introduction to Applied Data Science
  | 2022-2023
author: |
  | Christiana Kyritsi
  | c.kyritsi@students.uu.nl
  | http://www.github.com/yourgithubname
date: April 2023
urlcolor: purple
linkcolor: purple
output: 
  pdf_document
---

```{r setup, include = FALSE}
knitr::opts_chunk$set(warning = FALSE, message = FALSE, error=TRUE)
```

## Assignment 4: Collaborating Together 

### Part 1: Contributing to another student's Github repository

In this assignment, you will create a Github repository, containing this document and the .pdf output, which analyzes a dataset individually using some of the tools we have developed. 

This time, make sure to not only put your name and student e-mail in your Rmarkdown header, but also your Github account, as I have done myself. 

However, you will also pair up with a class mate and contribute to each others' Github repository. Each student is supposed to contribute to another student's work by writing a short interpretation of 1 or 2 sentences at the designated place (this place is marked with **designated place**) in the other student's assignment. 

This interpretation will not be graded, but a Github shows the contributors to a certain repository. This way, we can see whether you have contributed to a repository of a class mate. 

**Question 1.1**: Fill in the __github username__ of the class mate to whose repository you have contributed. 

[faradinaerd]

### Part 2: Analyzing various linear models

In this part, we will summarize a dataset and create a couple of customized tables. Then, we will compare a couple of linear models to each other, and see which linear model fits the data the best, and yields the most interesting results.

We will use a dataset called `GrowthSW` from the `AER` package. This is a dataset containing 65 observations on 6 variables and investigates the determinants of economic growth. First, we will try to summarize the data using the `modelsummary` package. 

```{r, warning=FALSE, message=FALSE}
library(AER)
data(GrowthSW)
```

One of the variables in the dataset is `revolutions`, the number of revolutions, insurrections and coup d'etats in country $i$ from 1965 to 1995.

**Question 2.1**: Using the function `datasummary`, summarize the mean, median, sd, min, and max of the variables `growth`, and `rgdp60` between two groups: countries with `revolutions` equal to 0, and countries with more than 0 revolutions. Call this variable `treat`. Make sure to also write the resulting data set to memory. Hint: you can check some examples [here](https://vincentarelbundock.github.io/modelsummary/articles/datasummary.html#datasummary).

```{r}
library(modelsummary); library(tidyverse)
GrowthSW <- GrowthSW %>%
  mutate(treat = ifelse(revolutions > 0, "more than 0", "equal to 0"))
datasummary<-datasummary(growth+rgdp60~treat*(Mean+Median+SD+Min+Max),data=GrowthSW)
datasummary(growth+rgdp60~treat*(Mean+Median+SD+Min+Max),data=GrowthSW)
```

**Designated place**: type one or two sentences describing this table of a fellow student below. For example, comment on the mean and median growth of both groups. Then stage, commit and push it to their github repository. 
```{r}
library(git2r)
git2r::config(user.name = "christianakyritsi", user.email = "christikyritsi@example.com")
git2r::init(path = "path_to_your_directory")
git2r::clone(url = "https://github.com/faradinaerd/repository.git", local_path = "path_to_clone_directory")
repo <- git2r::repository("path_to_clone_directory")
git2r::add(repo, "path_to_file1.R")
git2r::add(repo, "path_to_file2.R")
git2r::commit(repo, "Based on the provided data for the mean and median growth of both groups: Group with revolution equal to 0: The mean growth is 2.46, and the median growth is 2.29. This suggests that, on average, the group with growth equal to 0 has a moderate positive growth rate, as the mean is slightly higher than the median. Group with revolution more than 0: The mean growth is 1.68, and the median growth is 1.92. This indicates that, on average, the group with growth more than 0 has a slightly lower growth rate compared to the group with growth equal to 0, as both the mean and median values are lower.")
git2r::push(repo, "https://github.com/faradinaerd/repository.git")

```


### Part 3: Make a table summarizing reressions using modelsummary and kable

In question 2, we have seen that growth rates differ markedly between countries that experienced at least one revolution/episode of political stability and countries that did not. 

**Question 3.1**: Try to make this more precise this by performing a t-test on the variable growth according to the group variable you have created in the previous question. 

```{r}
t_test_result <- t.test(
  growth ~ treat,
  data = GrowthSW
)
print(t_test_result)
```

**Question 3.2**: What is the $p$-value of the test, and what does that mean? Write down your answer below.
#The p-value of the Welch Two Sample t-test is 0.06871. The p-value represents the probability of observing a test statistic as extreme as the one calculated, assuming the null hypothesis (no difference in means) is true. Since the p-value is greater than the significance level of 0.05, we do not have sufficient evidence to reject the null hypothesis and conclude that there is a significant difference between the means of the two groups.

We can also control for other factors by including them in a linear model, for example:

$$
\text{growth}_i = \beta_0 + \beta_1 \cdot \text{treat}_i + \beta_2 \cdot \text{rgdp60}_i + \beta_3 \cdot \text{tradeshare}_i + \beta_4 \cdot \text{education}_i + \epsilon_i
$$

**Question 3.3**: What do you think the purpose of including the variable `rgdp60` is? Look at `?GrowthSW` to find out what the variables mean. 
#The variable `rgdp60` in the linear model represents the real GDP per capita in 1960. Including this variable in the model allows us to control for the initial economic conditions of the countries. By including `rgdp60`, we can assess the effect of the treatment (`treat`) on the growth outcome (`growth`) while taking into account the differences in the initial economic conditions among the countries. The purpose is to examine whether the treatment effect remains statistically significant after accounting for the influence of the initial GDP per capita.


We now want to estimate a stepwise model. Stepwise means that we first estimate a univariate regression $\text{growth}_i = \beta_0 + \beta_1 \cdot \text{treat}_i + \epsilon_i$, and in each subsequent model, we add one control variable. 

**Question 3.4**: Write four models, titled `model1`, `model2`, `model3`, `model4` (using the `lm` function) to memory. Hint: you can also use the `update` function to add variables to an already existing specification.

```{r}
model1 <- lm(growth ~ treat, data = GrowthSW)
model2 <- lm(growth ~ treat+rgdp60, data = GrowthSW)
model3 <- lm(growth ~ treat+rgdp60+tradeshare, data = GrowthSW)
model4 <- lm(growth ~ treat+rgdp60+tradeshare+education, data = GrowthSW)
```

Now, we put the models in a list, and see what `modelsummary` gives us:

```{r}
list(model1, model2, model3, model4) |>
  modelsummary(stars = T,
#Editting this code to remove the statistics other than R Squared, as the next question 3.5 requires us to do so
#and N
gof_omit = 'R2 Adj. |AIC|BIC|Log.Lik|F|RMSE')

```

**Question 3.5**: Edit the code chunk above to remove many statistics from the table, but keep only the number of observations $N$, and the $R^2$ statistic. 

**Question 3.6**: According to this analysis, what is the main driver of economic growth? Why?
#According to the provided analysis, the main driver of economic growth is the variable "education." The coefficient estimate for "education" is statistically significant at the 1% level (***), indicating a strong positive relationship between education and economic growth. Other variables such as "treatmore than 0" (treatment effect) and "rgdp60" (initial GDP per capita) do not have statistically significant effects on economic growth, as their coefficient estimates are not significant at conventional significance levels. It is important to note that the analysis should be interpreted in the context of the specific dataset and model assumptions.

**Question 3.7**: In the code chunk below, edit the table such that the cells (including standard errors) corresponding to the variable `treat` have a red background and white text. Make sure to load the `kableExtra` library beforehand.

```{r}
library(kableExtra)
table <- list(model1, model2, model3, model4) |>
  modelsummary(stars = T, gof_map = c("nobs", "r.squared"))
table <- table |>
  row_spec(row = 3:4, background = "red", color = "white")
table

```

**Question 3.8**: Write a piece of code that exports this table (without the formatting) to a Word document. 

```{r}
library(kableExtra)
list(model1, model2, model3, model4) |>
  modelsummary(stars = T, gof_map = c("nobs", "r.squared"), output = 'table.docx')
```

## The End
